---
title: "Text Analysis Project- Compare speech of Eisenhower's & Nixon's"
author:
- Francesco Ignazio Re
- YinChia Huang
- Yue Wu
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

The State of the Union Address is an annual speech given by the U.S. President to a joint meeting of the U.S. Congress.  It summarizes the condition of the country and anticipates the future, especially the future legislation the President hopes that the congress will enact.
We analyze the text in these speeches, beginning with a sentiment analysis.  Use positive vs negative sentiment and the sentiments "joy,", "anger," and "anticipation."  


```{r include=FALSE}
library(tidytext)
library(dplyr)
library(tidyr)
library(readtext)
library(ggplot2)
library(gridExtra)
library(wordcloud)
library(reshape2)


eisenhower <- read.delim("eisenhower first state of the union.txt", header=FALSE)

#We create a paragraph for each line detected by read.delim and we tidy up the speech

eisenhower1 <- tibble(paragraph = 1:165, text = as.character(eisenhower$V1)) %>% 
  unnest_tokens(word, text)

#We count the recurrence of the same words in the same paragraph and we weigh them
#according to whether they have a positive or a negative influence

eis1 <- eisenhower1 %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word,index = paragraph %/% 2,sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)


plot1 <- ggplot(eis1, aes(index, sentiment) ) +
  geom_col(show.legend = FALSE) + labs(x = "Sentiment bars in Eisenhower's speech ")

```

## Sentiment bars in Eisenhower's speech
```{r}
plot1
```

```{r include=FALSE}
eis_words_count <- eisenhower1 %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word, sentiment, sort = TRUE)

plot2 <- eis_words_count %>% 
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment in Eisenhower's speech",
       x = NULL) +
  coord_flip()

```

## Contribution to sentiment in Eisenhower's speech
```{r}
plot2
```

## Word cloud in Eisenhower's speech
```{r}
eis1 %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```


```{r include=FALSE}
nixon <- read.delim("nixon first state of the union.txt", header=FALSE)

#We create a paragraph for each line detected by read.delim and we tidy up the speech

nixon1 <- tibble(paragraph = 1:132, text = as.character(nixon$V1)) %>% 
  unnest_tokens(word, text)

#We count the recurrence of the same words in the same paragraph and we weigh them
#according to whether they have a positive or a negative influence

nix1 <- nixon1 %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word,index = paragraph %/% 2,sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)


plot3 <- ggplot(nix1, aes(index, sentiment) ) +
  geom_col(show.legend = FALSE) + labs(x = "Sentiment bars in Nixon's speech ")

```

## Sentiment bars in Nixon's speech
```{r}
plot3 
```

```{r include=FALSE}
nix_words_count <- nixon1 %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word, sentiment, sort = TRUE)

plot4 <- nix_words_count %>% 
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment in Nixon's speech",
       x = NULL) +
  coord_flip()

```

## Contribution to sentiment in Nixon's speech
```{r}
plot4
```

## Word cloud in Nixon's speech

```{r}
nix1 %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```


## Analysis interpretation -1
```{r}
grid.arrange(plot1, plot3)
```

## Analysis interpretation -1
We can see that according to the way we decided to weigh the words Eisenhower's speech turned out to be much more engaging and dramatic as we can see peaks reaching values such as 15 and 10.
In Nixon's speech we see that the bars rarely exceed 4 and -4, resulting in a much more contained speech.


## Analysis interpretation - 2 
```{r}
grid.arrange(plot2,plot4)
```

## Analysis interpretation - 2 
By this second comparison, we can definitely see that both the speeches are built up on words that belong to a similar semantic context.
However in Eisenhower's speech we can recognize words such as 'defensive','attack', and 'tension' that reflect the historic period he was living in, trying to manage tensions under the looming threat of nuclear weapons with the Soviet Union. As a matter of fact, we don't find these words in Nixon's speech.

Analyzing the positive words, we can see that the first used words are about freedom and respect. 
Contrary to Nixon, Eisenhower favore a more moderate course of Republicanism, which preserved individual freedom and the marekt economy.


